---
title: "Homework 9"
author: "Brandon Simelgor"
date: "2023-04-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Brandon Simelgor
https://github.com/Simelgor05/Homework-9.git

```{r}
library(dplyr)

av <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/avengers/avengers.csv", stringsAsFactors = FALSE)
av
```

```{r}
parse_number <- function(column_name) {
  as.numeric(gsub("[^0-9]", "", column_name))
}
```

Get the data into a format where the five columns for Death[1-5] are replaced by two columnes: Time, and Death. Time should be a number between 1 and 5.
```{r}
death_columns <- grep("^Death", names(av))
deaths <- data.frame(Name = av$Name,
                     Time = sapply(names(av)[death_columns], parse_number),
                     Death = factor(ifelse(av[,death_columns] == "YES", "yes", ifelse(av[,death_columns] == "NO", "no", ""))))


```

Similarly, deal with the returns of characters.
```{r}
return_columns <- grep("^Return", names(av))
returns <- data.frame(Name = av$Name,
                      Time = sapply(names(av)[return_columns], parse_number),
                      Return = factor(ifelse(av[,return_columns] == "YES", "yes", ifelse(av[,return_columns] == "NO", "no", ""))))

```

Each team member picks one of the statements in the FiveThirtyEight analysis and fact checks it based on the data. Use dplyr functionality whenever possible.

If Iron Man fakes his death to chill out for a while but all his friends (and the reader) know he’s just kicking it somewhere, he didn’t die.
```{r}
deaths <- deaths %>%
  mutate(Name = if_else(Name == 'Anthony Edward "Tony" Stark', "Iron Man", Name))

IronManDeath <- deaths %>%
  filter(Name == "Iron Man") %>%
  pull(Death)
IronManDeath

IronManReturn <- returns %>% 
  filter(Name == "Iron Man") %>%
  pull(Return)
IronManReturn
```
If Iron man is seen dead but all his allies know he is not dead than he will not be marked as dead in the data and would also then not need to return which would mean the data is correct in showing that he only died once and returned once because this scenario does not mean he is dead according to the conditions for death mentioned in the article. 
